Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-22 ms.tex
Added score vs. magnification for all three datasets

% Discuss figure
In Figure~\ref{fig:scorevslensparams}, we show the classification
score as a function of image magnification for lens images in our
HST-like sample.  The left-hand side shows the relation color-coded by
the redshift of the lensing galaxy, and the right-hand side shows the
relation color-coded by the velocity dispersion of the lensing galaxy.
Lensing systems with images that have magnification $\gsim7$ will
almost certainly be classified as positive with threshold scores above
$\gsim0.5$.  These systems are also those that are most easily
classified by eye.  However, our trained model has varying performance
for systems with lower magnifications.

% Some dependence on redshift and velocity dispersion, which is folded
% into magnitude
Almost \todo{X\%} of lensing systems with magnifications $\lsim7$ will
be falsely identified as non-lenses for classification threshold
scores $\gsim0.5$.  These systems typically have lenses that are at
higher redshifts of $z\gsim0.5$ (lighter colors in left figure) and/or
velocity dispersions lower than $\sigma_v\lsim230.$~km/s (darker
colors in right figure).  Note that lensing galaxies with smaller
velocity dispersions are less massive and therefore have a smaller
efficiency of lensing cross section.  The smaller efficiency means
that a background galaxy is less likely to be strongly lensed with
high magnification.  Also, due to hierarchical structure formation,
galaxies are less massive at higher redshifts, so the trends of model
performance with these three parameters are somewhat degenerate with
one another.

@@

In a forthcoming paper, we will discuss how class imbalance, or
differences between the lens-model parameter distributions in the
training and test sets affect model performance and will explore a
method to correct for this.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
  \centering 
  \mbox{
    \subfigure{\includegraphics[width=\columnwidth,trim=0 0 0 0,
        clip]{figures/HST/or5ppc32cpb4/magnitude_d_colorcodedby_z.pdf}}\hfill
    \subfigure{\includegraphics[width=\columnwidth,trim=0 0 0 0,
        clip]{figures/HST/or5ppc32cpb4/magnitude_d_colorcodedby_velocity_dispersion.pdf}}
  } 
\caption{Image classification score on HST mock data as a function of
  lensed image magnification.  Left color-coded by redshift, right is
  color coded by the lens velocity dispersion.}
\label{fig:scorevslensparams}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% Discuss figure
In Figure~\ref{fig:scorevslensparams}, we show the classification
score as a function of image magnification of the source galaxy in
each of our samples.  In the top panel, each data point is color-coded
by the velocity dispersion of the lensing galaxy.  In the bottom
panel, the color-coding is by the redshift of the lens galaxy.  In
either an HST-like or LSST-like observation, lensing systems with
images that have magnification $\gsim7$ will almost certainly be
classified as positive with threshold scores above $\gsim0.5$.  These
systems are also those that are most easily classified by eye.
However, our trained model has varying performance for systems with
lower magnifications.

% Some dependence on redshift and velocity dispersion, which is folded
% into magnitude
In our mock HST sample, all but one of our lensing systems with
magnifications $\lsim7$ will be successfully identified for
classification threshold scores $\gsim0.5$.  These highly magnified
systems typically have lenses that are at higher redshifts of
$z\gsim0.5$ (lighter colors in bottom row) and/or lens galaxies with
velocity dispersions higher than $\sigma_v\lsim230.$~km/s (darker
colors in right figure).  Note that lensing galaxies with smaller
velocity dispersions are less massive and therefore have a smaller
efficiency of lensing cross section.  The smaller efficiency means
that a background galaxy is less likely to be strongly lensed with
high magnification.  Also, due to hierarchical structure formation,
galaxies are less massive at higher redshifts, so the trends of model
performance with these three parameters are somewhat degenerate with
one another.

@@

In a forthcoming paper, we will discuss how class imbalance, or
differences between the lens-model parameter distributions in the
training and test sets affect model performance and will explore a
method to correct for this.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
  \centering 
  \mbox{
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/HST_Magnification_Velocity_Dispersion.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST10_Magnification_Velocity_Dispersion.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST1_Magnification_Velocity_Dispersion.pdf}\hfill}
  }\\ 
  \mbox{
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/HST_Magnification_z.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST10_Magnification_z.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST1_Magnification_z.pdf}\hfill}
  }\\ 
\caption{Left to right: Image classification score on HST, LSST10,
  LSST1 mock observed lensing images as a function of lensed image
  magnification.  Top row: Each panel is color coded by the lens
  velocity dispersion in km/s.  High velocity dispersion lens galaxies
  are likely to produce high magnification images of the source
  galaxies.  Magnification is the strongest indicator of how likely a
  lensing system will be successfully classified.  Bottom row: Here,
  we color code by the redshift of the lens galaxy.}
\label{fig:scorevslensparams}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
